### 2022-02-03 sections/systematic_uncertainties.tex
updating EB comments
typo fix

The uncertainty on the pileup reweighting is evaluated by varying the pileup scale factors
by 1$\sigma$ based on the reweighting of the average interactions per bunch crossing. However, this
uncertainty is highly correlated with the luminosity uncertainty and may be an overestimate.

@@

%To estimate the uncertainty originating from ISR modelling in the single top samples, the same procedure as $t\bar{t}$ is used. One NP reflects the symmetrised effect of the two shower variations Var3cDown and Var3cUp, and the other NP with name ``scale'' describe the symmetrised effect from the independent variations of the renormalisation and factorisation scale. The impact of the uncertainty from FSR modelling is estimated by reweighting the nominal single top sample. The two variations $\mu^{FSR}_{R} \times 0.5$ and $\mu^{FSR}_{R} \times 2$ are considered.  The standard deviation of 100 NNPDF3.0nnlo variations is calculated Uncertainties on the PDF are evaluated following the recommended prescription in Ref.~\cite{ttRun2}.

@@

\begin{table}[htbp]
\caption{List of relative uncertainties of the signal strength from the combined fit in leptonic channel. The uncertainties are symmetrised for presentation and grouped into  the categories described in the text. %The quadrature sum of the individual uncertainties is not equal to the total uncertainty due to correlations introduced by the fit
}
\small
\centering
\begin{tabular}{cc} \toprule\toprule
$\text{Uncertainty}        $ & $  \Delta\mu/\mu[\%]  $\\\midrule
$\text{Fake modelling}     $ & $       2.1             $\\
$\text{Instrument}         $ & $       0.7             $\\
$\text{Jets}               $ & $       2.8             $\\
$\text{Met}                $ & $       1.2             $\\
$\text{Lepton}             $ & $       0.7             $\\
$\tau                      $ & $       2.3             $\\
$\text{b-tagging}          $ & $       4.8             $\\
$\text{Signal Theory}      $ & $       6.9             $\\
$\text{Other MC theory}    $ & $       2.1             $\\
$t\bar{t} \text{theory}    $ & $       3.7             $\\\midrule
$\text{Statistics}         $ & $       5.9             $\\
$\text{Total systematic}   $ & $       12.9            $\\\midrule
$\text{Total}              $ & $       14.2            $\\
\bottomrule\bottomrule
\end{tabular}
\label{tab:had_sys_impact}
\end{table}

>>>>

The uncertainty on the pileup reweighing is evaluated by varying the pileup scale factors
by 1$\sigma$ based on the reweighing of the average interactions per bunch crossing. However, this
uncertainty is highly correlated with the luminosity uncertainty and may be an overestimate.

@@

%To estimate the uncertainty originating from ISR modelling in the single top samples, the same procedure as $t\bar{t}$ is used. One NP reflects the symmetrised effect of the two shower variations Var3cDown and Var3cUp, and the other NP with name ``scale'' describe the symmetrised effect from the independent variations of the renormalisation and factorisation scale. The impact of the uncertainty from FSR modelling is estimated by reweighing the nominal single top sample. The two variations $\mu^{FSR}_{R} \times 0.5$ and $\mu^{FSR}_{R} \times 2$ are considered.  The standard deviation of 100 NNPDF3.0nnlo variations is calculated Uncertainties on the PDF are evaluated following the recommended prescription in Ref.~\cite{ttRun2}.

@@

\begin{table}[htbp]
\caption{List of relative uncertainties of the signal strength from the combined fit in leptonic channel. The uncertainties are symmetrised for presentation and grouped into  the categories described in the text. %The quadrature sum of the individual uncertainties is not equal to the total uncertainty due to correlations introduced by the fit
}
\small
\centering
\begin{tabular}{cc} \toprule\toprule
$\text{Uncertainty}        $ & $  \Delta\mu/\mu[\%]  $\\\midrule
$\text{Fake modelling}     $ & $       2.1             $\\
$\text{Instrument}         $ & $       0.7             $\\
$\text{Jets}               $ & $       2.8             $\\
$\text{Met}                $ & $       1.2             $\\
$\text{Lepton}             $ & $       0.7             $\\
$\tau                      $ & $       2.3             $\\
$\text{b-tagging}          $ & $       4.8             $\\
$\text{Signal Theory}      $ & $       6.9             $\\
$\text{Other MC theory}    $ & $       2.1             $\\
$t\bar{t} \text{theory}    $ & $       3.7             $\\\midrule
$\text{Statistics}         $ & $       5.9             $\\
$\text{Total systematic}   $ & $       12.9            $\\\midrule
$\text{Total}              $ & $       14.2            $\\
\bottomrule\bottomrule
\end{tabular}
\label{tab:lep_sys_impact}
\end{table}
